### 2019-12-05 article.tex
Materials And Models partially written

%\usepackage[authoryear,longnamesfirst]{natbib}
%\usepackage[authoryear]{natbib}
\usepackage[numbers]{natbib}
\usepackage{mathpazo}

@@

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Bayesian classification of Parkinson's disease patients using fMRI data}
\shortauthors{Amin Amini, Mayam Amirmazlaghani}

\title [mode = title]{Bayesian classification of Parkinson's disease patients using fMRI data}

@@

\subsection{Data acquisition}
fMRI scans were obtained from the OpenfMRI project which were acquired on a 3T Siemens Verio with repetition time (TR) = 2.5 s, echo time (TE) = 30ms, flip angle = 80°. Each sample contains 198 slices of 39×64×64 voxels from the brains of patients. Subjects were instructed to close their eyes and to rest quietly during the scan session \cite{OpenFmri}.

\subsection{Data pre-processing}
The fMRI data were pre-processed using the standard modules of FMRIB Software Library v5.0 \cite{FMRIB}. The pre-processing steps for the anatomical data involved motion correction (MCFLRIT), skull stripping, and spatial smoothing (Gaussian kernel of 5-mm FWHM). Low level noise was removed using a high-pass temporal filtering. The functional images were then aligned to the individual's high-resolution T1-weighted scans, which were subsequently registered to the Montreal Neurological Institute standard space (MNI152) using affine linear registration. and resampled at 2mm cubic voxels. The product of preprocessing step was used in the experiments.

>>>>

%\usepackage[authoryear,longnamesfirst]{natbib}
%\usepackage[authoryear]{natbib}
\usepackage[numbers]{natbib}
%\usepackage{mathpazo}

@@

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Classification of Parkinson's disease patients using Bayesian deep learning based on fMRI data}
\shortauthors{Amin Amini, Mayam Amirmazlaghani}

\title [mode = title]{Classification of Parkinson's disease patients using Bayesian deep learning based on fMRI data}

@@

\subsection{Data acquisition}
fMRI scans were obtained from the OpenfMRI project which was acquired on a 3T Siemens Verio with repetition time (TR) = 2.5 s, echo time (TE) = 30ms, flip angle = 80°. Each sample contains 198 slices of 39$\times$64$\times$64 voxels from the brains of patients. Subjects were instructed to close their eyes and to rest quietly during the scan session \cite{OpenFmri}.

\subsection{Data pre-processing}
The fMRI data were pre-processed using the standard modules of FMRIB Software Library v5.0 \cite{FMRIB}. The pre-processing steps for the anatomical data involved motion correction (MCFLRIT), skull stripping, and spatial smoothing (Gaussian kernel of 5-mm FWHM). Low level noise was removed using a high-pass temporal filtering. The functional images were then aligned to the individual's high-resolution T1-weighted scans, which were subsequently registered to the Montreal Neurological Institute standard space (MNI152) using affine linear registration. and resampled at 2mm cubic voxels. The product of the preprocessing step was used in the experiments.

\subsection{Three dimensional convolutional neural networks}
3D Convolutional Neural Networks which are inspired by human visual system are similar to classic neural networks. This architecture has been particularly designed based on the explicit assumption that raw data are three-dimensional that enables us to encode certain properties and also to reduce the amount of hyper parameters. The CNN topology utilizes spatial relationships to reduce the number of parameters which must be learned and thus improves upon general feed-forward back propagation training. Equation \eqref{eq:CnnVal} shows how value of each voxel is calculated from previous layer based on a fixed kernel \texttt{(size = P$\times$Q$\times$R)} and a bias for \texttt{j}th feature in \texttt{i}th layers where v is value, f is the activation function and w is filter weight \cite{Ji2013}.

\begin{equation}
v^{ xyz }_{ ij } = \\
f(  \\
b_{ij} +  \\
\sum_m \\ 
\sum_{p=0}^{P_i-1} \\
\sum_{q=0}^{Q_i-1} \\
\sum_{r=0}^{R_i-1} \\
\; w^{pqr}_{ijm}  \\
\; v ^ { (x+p)(y+q)(z+r) }_{ (i-1)m } \\
) \label{eq:CnnVal} 
\end{equation}

Since fMRI images are 3D time series and our experiment tries to find out if images contain any useful information despite their sequences, three dimensional CNN can be used as our computational core. A simple 3D CNN can be seen in Figure \ref{fig:CnnSample}

\begin{figure}
	\includegraphics[width=\linewidth]{images/3dCnn}
	\caption{3D CNN demonstration (kernel size = 3$\times$3$\times$3).}
	\label{fig:CnnSample}
\end{figure}

\subsection{Bayesian deep learning}
Deep learning has achieved significant success in many perception tasks including seeing (visual object recognition), reading (text understanding), and hearing (speech recognition). These are undoubtedly fundamental tasks for a functioning comprehensive artificial intelligence (AI) or data engineering (DE) system. However, in order to build a real AI/DE system, simply being able to see, read, and hear is far from enough. It should master
the ability of thinking.

Take medical diagnosis as an example. Besides seeing
visible symptoms (or medical images from MRI) and hearing descriptions from patients, a doctor has to look for relations among all the symptoms and preferably infer the corresponding etiology. Only after that can the doctor provide medical advice for the patients. In this example, although the abilities of seeing and hearing allow the doctor to acquire information from the patients, it is the thinking part that defines a doctor. Specifically, the ability of thinking here could involve causal inference, logic deduction, and dealing with uncertainty, which is apparently beyond the capability of conventional deep learning methods \cite{Wang2016}.

A neural network with arbitrary depth and non-linearities, with dropout applied before every weight layer, is mathematically equivalent to an approximation to the probabilistic deep Gaussian process \cite{Gal2016}.
